---
title: "telegramR"
author: "alisson soares"
date: "2023-12-16"
output:
  html_document: default
pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, build pacote}
# update a documentacao. 		- irá reconstruir NAMESPACE:
devtools::document() # rebuild docs and NAMESPACE
```

binary = FALSE this creates a tar.gz package that can be installed on any platform, provided they have a full development environment (although packages without source code can typically be installed out of the box).
If binary = TRUE, the package will have a platform specific extension (e.g. .zip for windows), and will only be installable on the current platform, but no development environment is needed.

```{r, build pacote}
# no console
# R CMD build senadoBrScraper
# ou
# devtools::build()
devtools::build(binary = FALSE)
Sys.time()
```

```{r, build pacote}
# Load complete package
devtools::load_all()
```

```{r, build pacote}
usethis::use_article()
# Set up test infrastructure with
usethis::use_testthat()
# Create a test file with
usethis::use_test("test_BRAParlSpeech")
# devtools::spell_check()
#☑ Write tests with test_that() and expect_().0
#☑ Run all tests with test() and run tests for current file with
devtools::test_active_file()

warnings()
```


```{r}
usethis::use_readme_rmd()
# devtools::build_readme()
```


```{r build, echo=FALSE, eval=FALSE}
devtools::build_readme()
```


```{r}
devtools::spell_check()
```


```{r, build pacote}
devtools::test()
```


```{r, build pacote}
devtools::check()
# 2 errors ✖ | 7 warnings ✖ | 3 notes ✖
```


```{r, build pacote}
#usethis::use_ccby_license().
#usethis:use_gpl_license(version = 3, include_future = TRUE)
# usethis:use_mit_license(version = 3, include_future = TRUE)
usethis::use_build_ignore("R/utils-pipe.R", escape = FALSE)
```


```{r, build pacote}
#usethis::use_warnings()
#(get_senate_links)
```

```{r}
# usethis::use_import_from("magrittr", "%>%")
# usethis::use_import_from("magrittr", "%$%")
```


```{r, build pacote}
devtools::check(document = FALSE, args = c('--as-cran'))
```


https://github.com/MangoTheCat/goodpractice

```{r}
goodpractice::gp("telegramR")
```


```{r}
usethis::use_vignette ("vignette-TelegramR") 
```

