---
title: "TelegramR - vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TelegramR - vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  comment = "#>"
)
```

The telegramR package deals with exported chats from [Telegram messenger](https://www.telegram.org/).
Telegram desktop allows the user to export the data of chats and channels, but how to extract ant treat those data remains a question.
This package allows the transformation of .HTML from exported chats/channels in tibble/dataframe, as well as have some functions to a brief summary about the exported chats. 
Check the [website](https://soaresalisson.github.io/telegramR/) or the [Github](https://github.com/SoaresAlisson/telegramR/)  of the project.

## Installation: Option 1 with {devtools} package
To install this package using devtools

```r
# installing devtools
install.packages("devtools")
# installing telegramR
devtools::install_github("SoaresAlisson/telegramR")
```

## Installation: Option 2 with {remotes} package

```r
# if remote package is installed, load it; If not, install
if (!require('remotes')) install.packages('remotes')
remotes::install_github('SoaresAlisson/telegramR')
```

## Installation: Option 3 download the files and build it locally

You go to Github, click on green bottom `<> code`, than in `Download Zip`, unzip it, open the .Rproj in Rstudio. Once the project is loaded, you can build the package: option1) press ctrl+shift+b, or 2) go to Build/Install Package

## Running the package

Once installed, to load the package:

```{r library}
library(telegramR)
```

You will need to have exported data from Telegram. Generally, it is at "Downloads/Telegram Desktop/"



To transform one .HTML file into tibble/dataframe, use the function `html2df("html_file")`

```{r, eval=FALSE}
# html2df("~/Downloads/Telegram Desktop/ChatExport_2023-12-16 (1)/messages.html")
html2df("../data/ChatExport_2023-03-17/messages.html" ) 
```

```{r, echo=FALSE, eval=TRUE}
chatExport <- system.file("extdata", "ChatExport_2024-03-17/messages.html", package="telegramR")
html2df(chatExport)
```

To get all messages from HTML in a master folder (usually `/Downloads/Telegram Desktop/`) and transform all in one single tibble, use `dir2df`. The function has the parameter `recursive = TRUE` as default, so it is possible to recursively find HTML files in folders inside another folders. 
It allows the user to organize its chats/channels per name in folders and subfolders.

```{r, eval=FALSE}
dirTelegram <- "~/Downloads/Telegram Desktop/"
dir2df(dirTelegram)
```

```{r, echo=FALSE, eval=TRUE}
dirTelegram <- system.file("extdata", package="telegramR")
dirTelegramDF <- dir2df(dirTelegram)
dirTelegramDF
```

```{r}
# Counting the messages per chat_name:
dplyr::count(dirTelegramDF, Chat_Name)
```

If you don't want it, use the parameter ` recursive = FALSE`. 

```{r dir2df}
dir2df(dirTelegram, recursive = FALSE)
```


## Organizing the exported chats/ channels.

Telegram Desktop allows the user to export channel/chats with specific date ranges.
If you exports a lot of telegram channels/chats, the probability to become lost are high. This confusion may happens because there is a lot of  groups/channels, or because the same channel was exported several times with different date ranges. To organize it, the function `tm_info()` (telegram information) returns the name of channel/chat, the first and the last dates in each HTML file

```{r}
info_all_tm_chats <- tm_info("~/Downloads/Telegram Desktop/")
info_all_tm_chats
```

In this way, if you want to export again the same chat, it is easy to know the last date of the last export. To make it even easier:

```{r}
filter_last_export(info_all_tm_chats)
```

But pay attention that if you export the same chat/channel at least twice, and with a time gap between them, the function `filter_last_export` will not identify this gap.
